---
title: "The attentive online reading: do eye movement modeling examples enhance navigation and evaluation of multiple documents in English (L2)?"
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_notebook:
    toc: yes
    toc_depth: 5
    number_sections: yes
  word_document:
    toc: yes
    toc_depth: '5'
bibliography: references.bib
csl: instituto-brasileiro-de-informacao-em-ciencia-e-tecnologia-abnt-initials.csl
---

# Preliminary Analyses

```{r include=FALSE}
# Load packages
library(tidyverse)    # Helper functions
library(lme4)         # Mixed-effect models
library(sjPlot)       # Model plotting
library(datawizard)   # Skewness and Kurtosis functions
library(jtools)       # APA theme
library(gridExtra)    # Multiple plots in one single image
library(openxlsx)     # Save file in xlsx format
library(RColorBrewer) # Colors

# Configure APA theme for figures
theme_set(theme_apa())

# Prevent scientific notation
options(scipen = 999)

# Load raw data - serp
serp = read.table('data/serp_sem_soma.csv', 
                 sep = ';', 
                 dec = ',',
                 encoding = 'UTF-8',
                 header = 1) %>%
  as_tibble()

# Load raw data - source_features
source_features = read.table('data/source_features_sem_soma.csv', 
                 sep = ';', 
                 encoding = 'UTF-8', 
                 header = 1) %>%
  as_tibble()

# Load raw data - relevant
relevant = read.table('data/relevant_sem_soma.csv',
                             sep = ';',
                             encoding = 'UTF-8',
                             header = 1) %>%
  as_tibble() %>%
  mutate(AOI = 'Reliable')

# Load raw data - irrelevant
irrelevant = read.table('data/irrelevant_sem_soma.csv',
               sep = ';',
               encoding = 'UTF-8',
               header = 1) %>%
      as_tibble() %>%
      mutate(AOI = 'Non-reliable')
```

## Outliers Detection and Replacement

Individual fixations that lasted two standart deviations above or below each participant fixation duration mean were considered outliers and were replaced by the participant fixation duration median[see @Salmeron2020, p. 1045]. Outliers represented 4.56% of the durations.

```{r message=FALSE, warning=FALSE, include=FALSE}

# Check outliers (individual fixations that lasted two SD above or below each student mean)
serp = serp %>% 
  group_by(Participant) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) | 
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))

source_features = source_features %>%
  group_by(Participant) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) |
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))

relevant = relevant %>%
  group_by(Participant, AOI) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) | 
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))

irrelevant = irrelevant %>%
  group_by(Participant, AOI) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) |
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))
```

```{r}
# Percentage of outliers

# 4.56%
c(serp$outlier,
  source_features$outlier,
  relevant$outlier,
  irrelevant$outlier) %>% mean()

```

```{r}
# Replace outlier with participant's median
serp = serp %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

source_features = source_features %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

relevant = relevant %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

irrelevant = irrelevant %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

# Sum the fixations
serp = serp %>%
  summarise(EventDuration = sum(Event.Duration..ms.))

source_features = source_features %>%
  summarise(EventDuration = sum(Event.Duration..ms.))

relevant = relevant  %>%
  summarise(EventDuration = sum(Event.Duration..ms.))

irrelevant = irrelevant %>% 
  summarise(EventDuration = sum(Event.Duration..ms.))
```

## Tests of Normality and Data Transformation

Figure 1 shows the frequency distributions of the time variables used in the study. All distributions have skewness values higher than 0.5, being right-skewed, as it is commonly observed with time variables. The variables were log-transformed to better approximated to a normal distribution. The log-transformed variables are shown in Figure 2 with their theoretical probability distributions. Transformation resulted in improved skewness values and, hence, more normally-distributed variables in three of the four variables. Thus, the log-transformed variables were used in the next steps of data analysis, except for Time spent reading realiable/non-reliable pages.

[see @Salmeron2020, p. 1047]

```{r echo=FALSE, message=FALSE, warning=FALSE}
hist_serp = serp %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Total fixation duration on the web page headers and snippets within the SERP', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 100000, 
             y = 8, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(serp$EventDuration)[1], 2))) +
    annotate('text', 
             x = 100000, 
             y = 7, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(serp$EventDuration)[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_source_features = source_features %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Total fixation duration on the source features', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 70000, 
             y = 8.5, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                source_features$EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 70000, 
             y = 7.5, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                source_features$EventDuration
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_reliable = relevant %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Time spent reading realiable pages',
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 450000, 
             y = 11, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                relevant$EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 450000, 
             y = 10, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                relevant$EventDuration
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_nonreliable = irrelevant %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Time spent reading non-reliable pages', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 450000, 
             y = 8, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                irrelevant$EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 450000, 
             y = 7, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                irrelevant$EventDuration
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

figure1 = arrangeGrob(hist_serp, 
                      hist_source_features, 
                      hist_reliable, 
                      hist_nonreliable, 
                      ncol = 2)

ggsave('figures/Figure1.png', 
       figure1,
       device = 'png', 
       width = 16, 
       height = 16, 
       units = 'cm', 
       dpi = 300)

grid.arrange(figure1)
```

*Figure 1*. Histograms of time variables

```{r echo=FALSE, message=FALSE, warning=FALSE}
serp = serp %>%
  mutate(log_EventDuration = log(EventDuration))

hist_log_serp = serp %>%
  ggplot(aes(log_EventDuration)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(mean = mean(serp$log_EventDuration), 
                            sd = sd(serp$log_EventDuration)),
                colour = 'red') +
  xlab(str_wrap('Natural logarithm of total length of fixations on the web page headers and snippets within the SERP',
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 11, 
           y = 1.1, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              serp$log_EventDuration)[1], 2))) +
  annotate('text', 
           x = 11, 
           y = 1, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              serp$log_EventDuration)[1], 2)))

source_features = source_features %>%
  mutate(log_EventDuration = log(EventDuration))

hist_log_source_features = source_features %>%
  ggplot(aes(log_EventDuration)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(
                  mean = mean(source_features$log_EventDuration), 
                  sd = sd(source_features$log_EventDuration)),
                colour = 'red') +
    xlab(str_wrap('Natural logarithm of total length of fixations on the source features', 
                  width = 32)) +
    ylab('Density') +
    annotate('text', 
             x = 11, 
             y = 1.45, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                source_features$log_EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 11, 
             y = 1.35, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                source_features$log_EventDuration
                                )[1], 2)))

hist_log_reliable = relevant %>%
  ggplot(aes(log(EventDuration))) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
              args = list(
                mean = mean(log(relevant$EventDuration)), 
                sd = sd(log(relevant$EventDuration))),
              colour = 'red') +
  xlab(str_wrap('Natural logarithm of time spent reading realiable pages',
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 12.7, 
           y = 1.85, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              log(relevant$EventDuration)
                              )[1], 2))) +
  annotate('text', 
           x = 12.7, 
           y = 1.7, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              log(relevant$EventDuration)
                              )[1], 2)))

irrelevant = irrelevant %>%
  mutate(log_EventDuration = 
           log(EventDuration))

hist_log_nonreliable = irrelevant %>%
  ggplot(aes(log_EventDuration)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(
                  mean = mean(irrelevant$log_EventDuration,
                              na.rm = T), 
                  sd = sd(irrelevant$log_EventDuration,
                          na.rm = T)),
                colour = 'red') +  
  xlab(str_wrap('Natural logarithm of time spent reading non-realiable pages', 
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 12.5, 
           y = 1.5, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              irrelevant$log_EventDuration
                              )[1], 2))) +
  annotate('text', 
           x = 12.5, 
           y = 1.4, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              irrelevant$log_EventDuration
                              )[1], 2)))

figure2 = arrangeGrob(hist_log_serp, 
                      hist_log_source_features, 
                      hist_log_reliable, 
                      hist_log_nonreliable, 
                      ncol = 2)

ggsave('figures/Figure2.png', 
       figure2,
       device = 'png', 
       width = 16, 
       height = 16, 
       units = 'cm', 
       dpi = 300)

grid.arrange(figure2)
```

*Figure 2*. Histograms of transformed time variables with theoretical probability distributions

```{r}
write_csv(serp, 'data/serp.csv')
write_csv(source_features, 'data/source_features.csv')
write_csv(relevant, 'data/reliable.csv')
write_csv(irrelevant, 'data/nonreliable.csv')

data = read.table('data/Variables_L2_EMME_clean_complete.csv', 
                 sep = ';', 
                 dec = ',',
                 encoding = 'UTF-8',
                 header = 1) %>%
  left_join(serp %>%
              rename(serp_clean = EventDuration,
                     serp_clean_log = log_EventDuration),
            by = 'Participant') %>%
  left_join(source_features %>%
              rename(source_features_clean = EventDuration,
                     source_features_clean_log = log_EventDuration),
            by = 'Participant') %>%
  left_join(relevant %>%
              rename(reliable = EventDuration) %>%
              select(-AOI),
            by = 'Participant') %>%
  left_join(irrelevant %>%
              rename(nonreliable = EventDuration) %>%
              select(c(Participant, nonreliable)),
            by = 'Participant') %>%
  mutate(group = ifelse(Participant %>% str_detect('EMME'), 
                        'EMME', 
                        'VIDEO'))

write.xlsx(data, 'data/data.xlsx')
```

# Main Analysis

## Research Question 1

To answer the research questions "RQ1a Do **EMME**s affect navigation across the results of a search engine research page (SERP) in English (L2), measured by **fixation duration on the webpage headers and snippets of each result within the SERP**? Do **L2 level** and **self-perceived strategic behavior** moderate this interaction between EMMEs and navigation in L2?", and "RQ1b Do **EMME**s affect source evaluation of multiple online documents in English (L2) that either endorse or refute the Learning Styles (LS) misconception, to be analyzed by the contrast between fixation duration on **reliable versus non-reliable pages**, and on **total fixation duration on the source features** (author's name and occupation)? Do **L2 level** and **self-perceived strategic behavior** moderate this interaction between EMMEs and evaluation of sources in L2?", two linear models were fit: the first one was a multiple linear regression model with the natural logarithm of fixation duration on the webpage headers and snippets of each result within the SERP as response and Group (two levels: EMME and VIDEO), L2 level and self-perceived strategic behavior as predictors; the second one was a mixed-effects model with total fixation duration on the source features on reliable and non-reliable pages as response and Group, L2 level and self-perceived strategic behavior as predictors with random intercepts for participants.

The first model shows no statistically significant effect when all the possible interactions are considered. When interactions are removed from the model, it shows a statistically significant effect of Group ($\beta=-0.67, p=0.001,95\% CI=[-1.06, -0.28], R^2=.19, R^2 adjusted=.15$).

The second model shows a similar pattern: no statistically significant effects when the interactions are considered and a statistically significant effect of Group ($\beta=56121.42, p=0.040,95\% CI=[2604.90, 109637.94], Marginal R^2=.12, Conditional R^2=.77$) when the interactions are removed from the model.

```{r include=FALSE}
# Fit model 1 for RQ1
rq1_model1 = data %>%
  lm(serp_clean_log ~ group + lextale + survey, data = .)
```

**Table 1**

*Total fixation duration on SERP predicted by Group, L2 level and self-perceived strategic behavior*

```{r echo=FALSE}
# Print table with statistical results
# tab_model(rq1_model1)
```

### Figure 3

```{r echo=FALSE}
# Plot model

figure3 = get_model_data(rq1_model1, 'eff')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .15) +
  xlab('Group') + 
  ylab('Fixation duration on SERP (log(ms))')

ggsave('figures/Figure3.png', 
       figure3,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure3
```

*Figure 3*. Log of total lenght of fixations predicted by Group

```{r include=FALSE}
# Fit model 2 for RQ1
rq1_model2 = data %>%
  pivot_longer(c(reliable, nonreliable), 
               names_to = 'reliability',
               values_to = 'duration') %>%
  lmer(duration ~ group + lextale + survey + (1|Participant), 
       data = .)
```

**Table 2**

*Total fixation duration on reliable and non-reliable pages predicted by Group, L2 level and self-perceived strategic behavior*

```{r echo=FALSE}
# Print table with statistical results
# tab_model(rq1_model2)
```

### Figure 4

```{r echo=FALSE}
# Plot model

figure4 = get_model_data(rq1_model2, 'pred')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .2) +
  xlab('Group') + 
  ylab(str_wrap(
    'Fixation duration on reliable/non-reliable pages (ms)',
    45))

ggsave('figures/Figure4.png', 
       figure4,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure4
```

*Figure 4*. Fixation duration on reliable/non-reliable pages predicted by Group

## Research Question 2

To answer the reserch questions "RQ2a Do **EMME**s enhance the identification of opposing perspectives about the Learning styles theory and criticism towards this misconception, as measured by an **essay writing task**? Do **English level**, **navigation and evaluation behavior** mediate the effect of EMMEs on argumentation score?", "RQ2b Do **EMME**s increase memory for the sources when reading multiple documents? Do **English level**, **navigation and evaluation behavior** mediate the effect of EMMEs on source memory?" and "RQ2c Are **EMME**s linked with updating of misconceptions about Learning Styles, to be measured in a **pre/posttest**? Do **English level**, **navigation and evaluation behavior** mediate the effect of EMMEs on misconception change?", two linear models were fit: the first with the log of total lenght of fixations on the source features as response and Group as predictors; and the second model with total lenght of fixations as response and Group, Realiability and the interaction between the two variables as predictors.

...

```{r include=FALSE}
# Fit model 1 for RQ2
rq2_model1 = data %>%
  lm(argumentation ~ group * lextale * serp_clean_log * source_features_clean_log, data = .)

# Fit model 2 for RQ2
rq2_model2 = data %>%
  lm(smt ~ group * lextale * serp_clean_log * source_features_clean_log, data = .)

# Fit model 3 for RQ2
rq2_model3 = data %>%
  pivot_longer(c(pre, post), 
               names_to = 'preposttest',
               values_to = 'response') %>%
  lmer(response ~ group + lextale + serp_clean_log + source_features_clean_log + preposttest + (1|Participant), 
       data = .)
```

**Table 2**

*...*

```{r echo=FALSE}
# Print table with statistical results
# tab_model(rq2_model1)
# tab_model(rq2_model2)
# tab_model(rq2_model3)
```

### Figure 5

```{r echo=FALSE}
# Plot model
figure5 = get_model_data(rq2_model1, 'eff')$serp_clean_log %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab('Argumentation score')

ggsave('figures/Figure5.png', 
       figure5,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure5
```

*Figure 5*. *Argumentation scores predicted by Fixation duration on SERP*

### Figure 6

```{r echo=FALSE}
# Plot model
figure6 = get_model_data(rq2_model1, 'eff')$source_features %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on the Source Features (log(ms))') + 
  ylab('Argumentation score')

ggsave('figures/Figure6.png', 
       figure6,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure6
```

*Figure 6*. *Argumentation score predicted by Fixation duraton on the Source Features*

### Figure 7

```{r}
# Plot model
figure7 = get_model_data(rq2_model1, 'int')[[4]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Argumentation score',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure7.png', 
       figure7,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure7
```

*Figure 7*. Interaction between Group and Fixation duration on source features

### Figure 8

```{r}
# Plot model
figure8 = get_model_data(rq2_model1, 'int')[[5]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Argumentation score',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure8.png', 
       figure8,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure8
```

*Figure 8*. Interaction between English level and Fixation duration on source features

### Figure 9

```{r}
# Plot model
figure9 = get_model_data(rq2_model1, 'int')[[6]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab(str_wrap(
    'Argumentation score',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure9.png', 
       figure9,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure9
```

*Figure 9*. Interaction between Fixation duration on SERP and Fixation duration on source features

### Figure 10

```{r}
# Plot model
figure10 = get_model_data(rq2_model2, 'eff')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .15) +
  xlab('Group') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure10.png', 
       figure10,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure10
```

*Figure 10*. Scores on the Source Memory Task predicted by Group

### Figure 11

```{r}
# Plot model
figure11 = get_model_data(rq2_model2, 'eff')$lextale %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure11.png', 
       figure11,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure11
```

*Figure 11*. Scores on the Source Memory Task predicted by English level

### Figure 12

```{r}
# Plot model
figure12 = get_model_data(rq2_model2, 'eff')$serp_clean_log %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure12.png', 
       figure12,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure12
```

*Figure 12*. Scores on the Source Memory Task predicted by Fixation duration on SERP

### Figure 13

```{r}
# Plot model
figure13 = get_model_data(rq2_model2, 'eff')$source_features_clean_log %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on the Source Features') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure13.png', 
       figure13,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure13
```

*Figure 13*. Scores on the Source Memory Task predicted by Fixation duration on the Source Features

### Figure 14

```{r}
# Plot model
figure14 = get_model_data(rq2_model2, 'int')[[1]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('English level',
                  18))

ggsave('figures/Figure14.png', 
       figure14,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure14
```

*Figure 14*. Interaction between Group and English level

### Figure 15

```{r}
# Plot model
figure15 = get_model_data(rq2_model2, 'int')[[2]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on SERP (log(ms))',
                  18))

ggsave('figures/Figure15.png', 
       figure15,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure15
```

*Figure 15*. Interaction between Group and Fixation duration on SERP

### Figure 16

```{r}
# Plot model
figure16 = get_model_data(rq2_model2, 'int')[[3]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on SERP (log(ms))',
                  18))

ggsave('figures/Figure16.png', 
       figure16,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure16
```

*Figure 16*. Interaction between English level and Fixation duration on SERP

### Figure 17

```{r}
# Plot model
figure17 = get_model_data(rq2_model2, 'int')[[4]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure17.png', 
       figure17,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure17
```

*Figure 17*. Interaction between Group and Fixation duration on source features

### Figure 18

```{r}
# Plot model
figure18 = get_model_data(rq2_model2, 'int')[[5]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure18.png', 
       figure18,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure18
```

*Figure 18*. Interaction between English level and Fixation duration on source features

### Figure 19

```{r}
# Plot model
figure19 = get_model_data(rq2_model2, 'int')[[6]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure19.png', 
       figure19,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure19
```

*Figure 19*. Interaction between Fixation duration on SERP and Fixation duration on source features

### Figure 20

```{r}
# Plot model
figure20 = get_model_data(rq2_model2, 'int')[[7]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO'),
         facet = facet %>% 
           str_replace_all('serp_clean_log',
                           'Fixation duration on SERP')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = 1)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('English level',
                  18)) + 
  facet_grid(cols = vars(facet))

ggsave('figures/Figure20.png', 
       figure20,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure20
```

*Figure 20*. Interaction between Group, English level and Fixation duration on SERP

### Figure 21

```{r}
# Plot model
plot_model(rq2_model2, type = 'int')[[8]]

figure21

ggsave('figures/Figure21.png', 
       figure21,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure21
```

### Figure 22

```{r}
# Plot model
plot_model(rq2_model2, type = 'int')[[9]]

figure22

ggsave('figures/Figure22.png', 
       figure22,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure22
```

### Figure 23

```{r}
# Plot model
plot_model(rq2_model2, type = 'int')[[10]]

figure23

ggsave('figures/Figure23.png', 
       figure23,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure23
```

### Figure 24

```{r}
# Plot model
plot_model(rq2_model2, type = 'int')[[11]]

figure24

ggsave('figures/Figure24.png', 
       figure24,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure24
```

### References
