---
title: "The attentive online reading: do eye movement modeling examples enhance navigation and evaluation of multiple documents in English (L2)?"
output:
  word_document:
    toc: yes
    toc_depth: '5'
  html_notebook:
    toc: yes
    toc_depth: 5
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
bibliography: references.bib
csl: instituto-brasileiro-de-informacao-em-ciencia-e-tecnologia-abnt-initials.csl
---

# Preliminary Analyses

```{r message=FALSE, warning=FALSE, include=FALSE}
# Load packages
library(tidyverse)    # Helper functions
library(lme4)         # Mixed-effect models
library(sjPlot)       # Model plotting
library(datawizard)   # Skewness and Kurtosis functions
library(jtools)       # APA theme
library(gridExtra)    # Multiple plots in one single image
library(openxlsx)     # Save file in xlsx format
library(RColorBrewer) # Colors
library(mediation)    # Mediation analysis

# Configure APA theme for figures
theme_set(theme_apa())

# Prevent scientific notation
options(scipen = 999)

# Load raw data - serp
serp_raw = read.table('data/serp_sem_soma.csv', 
                 sep = ';', 
                 dec = ',',
                 encoding = 'UTF-8',
                 header = 1) %>%
  as_tibble()

# Load raw data - source features
source_features_raw = read.xlsx('data/source_features_sem_soma.xlsx')

# Load raw data - reliable and non-reliable
reliable_nonreliable_raw = read.xlsx('data/reliable_nonreliable_sem_soma.xlsx')
```

## Outliers Detection and Replacement

Individual fixations that lasted two standart deviations above or below each participant fixation duration mean were considered outliers and were replaced by the participant fixation duration median[see @Salmeron2020, p. 1045]. Outliers represented 4.56% of the durations.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Check outliers (individual fixations that lasted two SD above or below each student mean)
serp_raw = serp_raw %>% 
  group_by(Participant) %>%
  mutate(M = mean(EventDuration),
         SD = sd(EventDuration),
         outlier = EventDuration > M + (2 * SD) | 
           EventDuration < M - (2 * SD),
         Median = median(EventDuration))

source_features_raw = source_features_raw %>%
  group_by(Participant) %>%
  mutate(M = mean(EventDuration),
         SD = sd(EventDuration),
         outlier = EventDuration > M + (2 * SD) |
           EventDuration < M - (2 * SD),
         Median = median(EventDuration))

reliable_nonreliable_raw = reliable_nonreliable_raw %>%
  group_by(Participant) %>%
  mutate(M = mean(EventDuration),
         SD = sd(EventDuration),
         outlier = EventDuration > M + (2 * SD) | 
           EventDuration < M - (2 * SD),
         Median = median(EventDuration))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Percentage of outliers

# 4.56%
c(serp_raw$outlier,
  source_features_raw$outlier,
  reliable_nonreliable_raw$outlier) %>% mean()
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Replace outlier with participant's median
serp_raw = serp_raw %>%
  mutate(EventDuration = 
           ifelse(outlier, Median, EventDuration))

source_features_raw = source_features_raw %>%
  mutate(EventDuration = 
           ifelse(outlier, Median, EventDuration))

reliable_nonreliable_raw = reliable_nonreliable_raw %>%
  mutate(EventDuration = 
           ifelse(outlier, Median, EventDuration))

# Get the mean of EventDuration per text (reliable/nonreliable)
reliable_nonreliable = reliable_nonreliable_raw %>%
  group_by(Participant, Text) %>%
  summarise(EventDuration = sum(EventDuration),
            Words = unique(Words)) %>%
  summarise(EventDuration = EventDuration/Words,
            Text = unique(Text)) %>%
  mutate(Reliability = ifelse(Text %in% c(1, 3, 5), 'Nonreliable', 'Reliable'))

# Get the mean of EventDuration per word
serp = serp_raw %>%
  group_by(Participant) %>%
  summarise(EventDuration = sum(EventDuration)/233)

source_features = source_features_raw %>%
  group_by(Participant) %>%
  summarise(EventDuration = sum(EventDuration)/60)

reliable_nonreliable = reliable_nonreliable %>%
  group_by(Participant, Reliability) %>%
  summarise(EventDuration = mean(EventDuration)) %>%
  pivot_wider(names_from = Reliability, values_from = EventDuration)

# Write data
write.xlsx(serp, 'data/serp_final.xlsx')

write.xlsx(source_features, 'data/source_features_final.xlsx')

write.xlsx(reliable_nonreliable, 'data/reliable_nonreliable_final.xlsx')
```

## Tests of Normality and Data Transformation

```{r message=FALSE, warning=FALSE, include=FALSE}
data_final = read.xlsx('data/data_final.xlsx')
```

Figure 1 shows the frequency distributions of the time variables used in the study. Apart from mean fixation duration on reliable pages, all distributions have skewness values higher than 0.5, being right-skewed, as it is commonly observed with time variables. The variables were log-transformed to be better approximated to a normal distribution. The log-transformed variables are shown in Figure 2 with their theoretical probability distributions. Transformation resulted in improved skewness values for two of the four variables, namely, total fixation duration on serp and total fixation duration on source features. Thus, log-transformed variables were used for these two variables.

[see @Salmeron2020, p. 1047]

```{r echo=FALSE, message=FALSE, warning=FALSE}
hist_serp = data_final %>%
    ggplot(aes(serp_clean_per_word)) +
    geom_histogram() +
    xlab(str_wrap('Mean fixation duration on the web page headers and snippets within the SERP', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 400, 
             y = 7, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(data_final$serp_clean_per_word)[1], 2))) +
    annotate('text', 
             x = 400, 
             y = 6, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(data_final$serp_clean_per_word)[1], 2)))

hist_source_features = data_final %>%
    ggplot(aes(source_features_per_word)) +
    geom_histogram() +
    xlab(str_wrap('Mean fixation duration on the source features', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 600, 
             y = 7, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                data_final$source_features_per_word
                                )[1], 2))) +
    annotate('text', 
             x = 600, 
             y = 6, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                data_final$source_features_per_word
                                )[1], 2)))

hist_reliable = data_final %>%
    ggplot(aes(reliable_per_word)) +
    geom_histogram() +
    xlab(str_wrap('Mean fixation duration on realiable pages',
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 350, 
             y = 8, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                data_final$reliable_per_word
                                )[1], 2))) +
    annotate('text', 
             x = 350, 
             y = 7, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                data_final$reliable_per_word
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_nonreliable = data_final %>%
    ggplot(aes(nonreliable_per_word)) +
    geom_histogram() +
    xlab(str_wrap('Mean fixation duration on non-reliable pages', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 400, 
             y = 6, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                data_final$nonreliable_per_word
                                )[1], 2))) +
    annotate('text', 
             x = 400, 
             y = 5, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                data_final$nonreliable_per_word
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

figure1 = arrangeGrob(hist_serp, 
                      hist_source_features, 
                      hist_reliable, 
                      hist_nonreliable, 
                      ncol = 2)

ggsave('figures/Figure1.png', 
       figure1,
       device = 'png', 
       width = 16, 
       height = 16, 
       units = 'cm', 
       dpi = 300)

grid.arrange(figure1)

```

*Figure 1*. Histograms of time variables

```{r echo=FALSE, message=FALSE, warning=FALSE}
data_final = data_final %>%
  mutate(log_serp = log(serp_clean_per_word),
         log_source_features = log(source_features_per_word),
         log_reliable = log(reliable_per_word),
         log_nonreliable = log(nonreliable_per_word))

hist_log_serp = data_final %>%
  ggplot(aes(log_serp)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(mean = mean(data_final$log_serp), 
                            sd = sd(data_final$log_serp)),
                colour = 'red') +
  xlab(str_wrap('Natural logarithm of mean fixation duration on the web page headers and snippets within the SERP',
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 4, 
           y = 0.85, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              data_final$log_serp)[1], 2))) +
  annotate('text', 
           x = 4, 
           y = 0.75, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              data_final$log_serp)[1], 2)))

hist_log_source_features = data_final %>%
  ggplot(aes(log_source_features)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(
                  mean = mean(data_final$log_source_features), 
                  sd = sd(data_final$log_source_features)),
                colour = 'red') +
    xlab(str_wrap('Natural logarithm of mean fixation duration on the source features', 
                  width = 32)) +
    ylab('Density') +
    annotate('text', 
             x = 4, 
             y = 0.7, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                data_final$log_source_features
                                )[1], 2))) +
    annotate('text', 
             x = 4, 
             y = 0.6, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                data_final$log_source_features
                                )[1], 2)))

hist_log_reliable = data_final %>%
  ggplot(aes(log_reliable)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
              args = list(
                mean = mean(data_final$log_reliable), 
                sd = sd(data_final$log_reliable)),
              colour = 'red') +
  xlab(str_wrap('Natural logarithm of time spent reading realiable pages',
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 4.5, 
           y = 2, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              data_final$log_reliable
                              )[1], 2))) +
  annotate('text', 
           x = 4.5, 
           y = 1.5, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              data_final$log_reliable
                              )[1], 2)))

hist_log_nonreliable = data_final %>%
  ggplot(aes(log_nonreliable)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(
                  mean = mean(data_final$log_nonreliable,
                              na.rm = T), 
                  sd = sd(data_final$log_nonreliable,
                          na.rm = T)),
                colour = 'red') +  
  xlab(str_wrap('Natural logarithm of time spent reading non-realiable pages', 
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 4, 
           y = 1.2, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              data_final$log_nonreliable
                              )[1], 2))) +
  annotate('text', 
           x = 4, 
           y = 1, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              data_final$log_nonreliable
                              )[1], 2)))

figure2 = arrangeGrob(hist_log_serp, 
                      hist_log_source_features, 
                      hist_log_reliable, 
                      hist_log_nonreliable, 
                      ncol = 2)

ggsave('figures/Figure2.png', 
       figure2,
       device = 'png', 
       width = 16, 
       height = 16, 
       units = 'cm', 
       dpi = 300)

grid.arrange(figure2)
```

*Figure 2*. Histograms of transformed time variables with theoretical probability distributions

```{r message=FALSE, warning=FALSE, include=FALSE}
data_final = data_final %>%
  dplyr::select(-c(serp_clean_per_word, log_source_features, log_reliable, log_nonreliable))

write.xlsx(data_final, 'data/data_final_transformed.xlsx')
```

```{r message=FALSE, warning=FALSE, include=FALSE}
data_final_transformed = read.xlsx(
  'data/data_final_transformed.xlsx')
```

# Main Analysis

## Descriptive statistics

```{r}
# Adicionar tabela com resumo das variáveis:
# Média, desvio padrão, simetria, kurtose, mínimo, máximo (por grupo)
```


## Research Questions 1a and 1b

### RQ1a

"RQ1a: Do EMMEs affect navigation across the results of a search engine research page (SERP) in English (L2), measured by fixation duration on the webpage headers and snippets of each result within the SERP? Do L2 level and self-perceived strategic behavior mediate this interaction between EMMEs and navigation in L2?"

To answer these research questions a mediation analysis was conducted. First, a simple linear regression model was fit with fixation duration on SERP (log transformed) as response and Group (two levels: Control and Experimental) as predictor. This model show a statistically significant effect of Group ($\beta=0.68, p=.001, 95\%~CI=[0.30, 1.06], R^2=.19, Adjusted~R^2=.18$). Then, the effects of Group on L2 level and Self-reported behaviour were analyzed to verify possible mediation effects with two linear models, both with Group as predictor and each one with a mediator as response. The models show that there is no effect of Group on L2 level ($beta=1.20, p=.614, 95\%~CI=[-3.54,5.93], R^2=.005, Adjusted~R^2=-.01$) nor on Self-reported behaviour ($\beta=-0.14,p=.179, 95\%~CI=[-0.34, 0.06, R^2=.03, Adjusted~R^2=0.02]$). So, the effect of Group is not mediated by these factors.



```{r message=FALSE, warning=FALSE, include=FALSE}
# Total effect for RQ1a
rq1a_total = data_final_transformed %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(log_serp ~ group, data = .)

tab_model(rq1a_total)

# Effect of predictor onto mediator1
rq1a_mediator1 = data_final_transformed %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(lextale ~ group, data = .)

tab_model(rq1a_mediator1)

# Effect of predictor onto mediator2
rq1a_mediator2 = data_final_transformed %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(survey ~ group, data = .)

tab_model(rq1a_mediator2)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
figure3 = get_model_data(rq1a_total, type = 'eff')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'Control', `2` = 'Experimental')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .15) +
  xlab('Group') + 
  ylab('Fixation duration on SERP (log(ms))')

ggsave('figures/Figure3.png', 
       figure3,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure3
```

### RQ1b

"Do EMMEs affect source evaluation of multiple online documents in English (L2) that either endorse or refute the Learning Styles (LS) misconception, to be analyzed by the contrast between fixation duration on reliable versus non-reliable pages, and on total fixation duration on the source features (author’s name and occupation)?  Do L2 level and self-perceived strategic behavior mediate this interaction between EMMEs and evaluation of sources in L2?"

To answer these questions a mediation analysis was performed. First, a multiple linear mixed-effects model was fit with Fixation duration on reliable and non-reliable pages as response, reliability (two levels: Reliable and Non-reliable), Group (two levels: Control and Experimental) and their interaction as predictors and random intercepts for participants. The model shows a statistically significant effect of Group ($\beta=-43.57, p=.044, 95\%~CI=[-85.99, -1.16], Marginal~R^2=.07, Conditional~R^2=.83$) but not of Reliability ($\beta=6.37, p=.369, 95\%~CI=[-7.63, 20.36]$). It also shows a statistically significant interaction between Group and Reliability ($\beta=29.39, p=.034, 95%~CI=[2.26, 56.52]$). Since there are no effects of Group on L2 level nor Self-perceived behaviour, no additional steps were conducted. No mediation effects were observed with this model. Then, a linear model was fit with Fixation duration on source features as response and Group predictor. The model shows no statistically significant effects of Group ($\beta=-60.29, p=.174, 95\%~CI=[-148.07, 27.49], R^2=0.03, Adjusted~R^2=0.02$) and, thus, no additional steps were necessary.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Total effect for RQ1b, Model 1
rq1b_model1_total = data_final_transformed %>%
  pivot_longer(c(reliable_per_word, nonreliable_per_word), 
               names_to = 'reliability', 
               values_to = 'fixation') %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lmer(fixation ~ reliability * group + (1|Participant), data = .)

tab_model(rq1b_model1_total)

# Total effect for RQ1b, Model 2
rq1b_model2_total = data_final_transformed %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(source_features_per_word ~ group, data = .)

tab_model(rq1b_model2_total)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
figure4 = get_model_data(rq1b_model1_total, type = 'int') %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'Non-reliable', `2` = 'Reliable'),
         group = group %>%
           as_factor() %>%
           recode('VIDEO' = 'Control', 'EMME' = 'Experimental')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = 1)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Fixation duration on reliable and non-reliable pages',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Reliability',
                  18))

ggsave('figures/Figure4.png', 
       figure4,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure4
```

## Research Questions 2a, 2b and 2c

### RQ2a

"RQ2a Do EMMEs enhance argumentative reasoning, i.e., identification of opposing perspectives about the Learning styles theory, as measured by an essay writing task? Do English level, navigation and evaluation behavior mediate the effect of EMMEs on argumentation score?"

To answer these questions a mediation analysis was performed. A linear model with Argumentation scores on an essay writing task as response and Group as predictor. No effect of Group was observed $\beta=0.19, p=.683, 95\%~CI=[-0.75, 1.14], R^2=.003, Adjusted R^2=-.015$. Since there was no effect of Group, the additional steps were not performed.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Total effect for RQ2a
rq2a_model_total = data_final_transformed %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(argumentationNew ~ group, data = .)

tab_model(rq2a_model_total)
```

### RQ2b

"RQ2b Do EMMEs increase memory for the sources when reading multiple documents? Do English level, navigation and evaluation behavior mediate the effect of EMMEs on source memory?"

To answer these questions a mediation analysis was performed. A linear model with Source memory task scores as response and Group as predictor. No effect of Group was observed $\beta=-1.39, p=.187, 95\%~CI=[-3.48, 0.70], R^2=.031, Adjusted R^2=-.014$. Since there was no effect of Group, the additional steps were not performed.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Total effect for RQ2b
rq2b_model_total = data_final_transformed %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(smt ~ group, data = .)

tab_model(rq2b_model_total)
```

### RQ2c

"RQ 2c Are EMMEs linked with updating of misconceptions about Learning Styles, to be measured in a pre/posttest? Do English level, navigation, and evaluation behavior (including memory for the sources) mediate the effect of EMMEs on misconception change?"

To answer these questions a mediation analysis was performed. A linear model with Scores on a pre and post-test of misconceptions about learning styles as response and Group as predictor. No effect of Group was observed $\beta=0.46, p=.218, 95\%~CI=[-0.28, 1.20], R^2=.014, Adjusted R^2=-.005$. Since there was no effect of Group, the additional steps were not performed.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Total effect for RQ2c
rq2c_model_total = data_final_transformed %>%
  pivot_longer(c(pre, post),
               names_to = 'moment',
               values_to = 'score') %>%
  mutate(group = group %>% 
           as_factor()  %>%
           relevel('VIDEO')) %>%
  lm(score ~ group, data = .)

tab_model(rq2c_model_total)
```

