---
title: "The attentive online reading: do eye movement modeling examples enhance navigation and evaluation of multiple documents in English (L2)?"
output:
  word_document:
    toc: yes
    toc_depth: '5'
  html_notebook:
    toc: yes
    toc_depth: 5
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '5'
bibliography: references.bib
csl: instituto-brasileiro-de-informacao-em-ciencia-e-tecnologia-abnt-initials.csl
---

# Preliminary Analyses

```{r message=FALSE, warning=FALSE, include=FALSE}
# Load packages
library(tidyverse)    # Helper functions
library(lme4)         # Mixed-effect models
library(sjPlot)       # Model plotting
library(datawizard)   # Skewness and Kurtosis functions
library(jtools)       # APA theme
library(gridExtra)    # Multiple plots in one single image
library(openxlsx)     # Save file in xlsx format
library(RColorBrewer) # Colors

# Configure APA theme for figures
theme_set(theme_apa())

# Prevent scientific notation
options(scipen = 999)

# Load raw data - serp
serp = read.table('data/serp_sem_soma.csv', 
                 sep = ';', 
                 dec = ',',
                 encoding = 'UTF-8',
                 header = 1) %>%
  as_tibble()

# Load raw data - source_features
source_features = read.table('data/source_features_sem_soma.csv', 
                 sep = ';', 
                 encoding = 'UTF-8', 
                 header = 1) %>%
  as_tibble()

# Load raw data - relevant
relevant = read.table('data/relevant_sem_soma.csv',
                             sep = ';',
                             encoding = 'UTF-8',
                             header = 1) %>%
  as_tibble() %>%
  mutate(AOI = 'Reliable')

# Load raw data - irrelevant
irrelevant = read.table('data/irrelevant_sem_soma.csv',
               sep = ';',
               encoding = 'UTF-8',
               header = 1) %>%
      as_tibble() %>%
      mutate(AOI = 'Non-reliable')
```

## Outliers Detection and Replacement

Individual fixations that lasted two standart deviations above or below each participant fixation duration mean were considered outliers and were replaced by the participant fixation duration median[see @Salmeron2020, p. 1045]. Outliers represented 4.56% of the durations.

```{r message=FALSE, warning=FALSE, include=FALSE}

# Check outliers (individual fixations that lasted two SD above or below each student mean)
serp = serp %>% 
  group_by(Participant) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) | 
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))

source_features = source_features %>%
  group_by(Participant) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) |
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))

relevant = relevant %>%
  group_by(Participant, AOI) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) | 
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))

irrelevant = irrelevant %>%
  group_by(Participant, AOI) %>%
  mutate(M = mean(Event.Duration..ms.),
         SD = sd(Event.Duration..ms.),
         outlier = Event.Duration..ms. > M + (2 * SD) |
           Event.Duration..ms. < M - (2 * SD),
         Median = median(Event.Duration..ms.))
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Percentage of outliers

# 4.56%
c(serp$outlier,
  source_features$outlier,
  relevant$outlier,
  irrelevant$outlier) %>% mean()

```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Replace outlier with participant's median
serp = serp %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

source_features = source_features %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

relevant = relevant %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

irrelevant = irrelevant %>%
  mutate(Event.Duration..ms. = 
           ifelse(outlier, Median, Event.Duration..ms.))

# Sum the fixations
serp = serp %>%
  summarise(EventDuration = sum(Event.Duration..ms.))

source_features = source_features %>%
  summarise(EventDuration = sum(Event.Duration..ms.))

relevant = relevant  %>%
  summarise(EventDuration = sum(Event.Duration..ms.))

irrelevant = irrelevant %>% 
  summarise(EventDuration = sum(Event.Duration..ms.))
```

## Tests of Normality and Data Transformation

Figure 1 shows the frequency distributions of the time variables used in the study. All distributions have skewness values higher than 0.5, being right-skewed, as it is commonly observed with time variables. The variables were log-transformed to be better approximated to a normal distribution. The log-transformed variables are shown in Figure 2 with their theoretical probability distributions. Transformation resulted in improved skewness values for two of the four variables, namely, total fixation duration on serp and total fixation duration on source features. Thus, log-transformed variables were used for these two variables.

[see @Salmeron2020, p. 1047]

```{r echo=FALSE, message=FALSE, warning=FALSE}
hist_serp = serp %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Total fixation duration on the web page headers and snippets within the SERP', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 100000, 
             y = 8, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(serp$EventDuration)[1], 2))) +
    annotate('text', 
             x = 100000, 
             y = 7, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(serp$EventDuration)[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_source_features = source_features %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Total fixation duration on the source features', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 70000, 
             y = 8.5, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                source_features$EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 70000, 
             y = 7.5, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                source_features$EventDuration
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_reliable = relevant %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Time spent reading realiable pages',
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 450000, 
             y = 11, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                relevant$EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 450000, 
             y = 10, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                relevant$EventDuration
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

hist_nonreliable = irrelevant %>%
    ggplot(aes(EventDuration)) +
    geom_histogram() +
    xlab(str_wrap('Time spent reading non-reliable pages', 
                  width = 32)) +
    ylab('Frequency') +
    annotate('text', 
             x = 450000, 
             y = 8, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                irrelevant$EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 450000, 
             y = 7, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                irrelevant$EventDuration
                                )[1], 2))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
  

figure1 = arrangeGrob(hist_serp, 
                      hist_source_features, 
                      hist_reliable, 
                      hist_nonreliable, 
                      ncol = 2)

ggsave('figures/Figure1.png', 
       figure1,
       device = 'png', 
       width = 16, 
       height = 16, 
       units = 'cm', 
       dpi = 300)

grid.arrange(figure1)
```

*Figure 1*. Histograms of time variables

```{r echo=FALSE, message=FALSE, warning=FALSE}
serp = serp %>%
  mutate(log_EventDuration = log(EventDuration))

hist_log_serp = serp %>%
  ggplot(aes(log_EventDuration)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(mean = mean(serp$log_EventDuration), 
                            sd = sd(serp$log_EventDuration)),
                colour = 'red') +
  xlab(str_wrap('Natural logarithm of total length of fixations on the web page headers and snippets within the SERP',
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 11, 
           y = 1.1, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              serp$log_EventDuration)[1], 2))) +
  annotate('text', 
           x = 11, 
           y = 1, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              serp$log_EventDuration)[1], 2)))

source_features = source_features %>%
  mutate(log_EventDuration = log(EventDuration))

hist_log_source_features = source_features %>%
  ggplot(aes(log_EventDuration)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(
                  mean = mean(source_features$log_EventDuration), 
                  sd = sd(source_features$log_EventDuration)),
                colour = 'red') +
    xlab(str_wrap('Natural logarithm of total length of fixations on the source features', 
                  width = 32)) +
    ylab('Density') +
    annotate('text', 
             x = 11, 
             y = 1.45, 
             label = paste0('Skewness: ', 
                            round(
                              skewness(
                                source_features$log_EventDuration
                                )[1], 2))) +
    annotate('text', 
             x = 11, 
             y = 1.35, 
             label = paste0('Kurtosis: ', 
                            round(
                              kurtosis(
                                source_features$log_EventDuration
                                )[1], 2)))

hist_log_reliable = relevant %>%
  ggplot(aes(log(EventDuration))) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
              args = list(
                mean = mean(log(relevant$EventDuration)), 
                sd = sd(log(relevant$EventDuration))),
              colour = 'red') +
  xlab(str_wrap('Natural logarithm of time spent reading realiable pages',
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 12.7, 
           y = 1.85, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              log(relevant$EventDuration)
                              )[1], 2))) +
  annotate('text', 
           x = 12.7, 
           y = 1.7, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              log(relevant$EventDuration)
                              )[1], 2)))

irrelevant = irrelevant %>%
  mutate(log_EventDuration = 
           log(EventDuration))

hist_log_nonreliable = irrelevant %>%
  ggplot(aes(log_EventDuration)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dnorm, 
                args = list(
                  mean = mean(irrelevant$log_EventDuration,
                              na.rm = T), 
                  sd = sd(irrelevant$log_EventDuration,
                          na.rm = T)),
                colour = 'red') +  
  xlab(str_wrap('Natural logarithm of time spent reading non-realiable pages', 
                width = 32)) +
  ylab('Density') +
  annotate('text', 
           x = 12.5, 
           y = 1.5, 
           label = paste0('Skewness: ', 
                          round(
                            skewness(
                              irrelevant$log_EventDuration
                              )[1], 2))) +
  annotate('text', 
           x = 12.5, 
           y = 1.4, 
           label = paste0('Kurtosis: ', 
                          round(
                            kurtosis(
                              irrelevant$log_EventDuration
                              )[1], 2)))

figure2 = arrangeGrob(hist_log_serp, 
                      hist_log_source_features, 
                      hist_log_reliable, 
                      hist_log_nonreliable, 
                      ncol = 2)

ggsave('figures/Figure2.png', 
       figure2,
       device = 'png', 
       width = 16, 
       height = 16, 
       units = 'cm', 
       dpi = 300)

grid.arrange(figure2)
```

*Figure 2*. Histograms of transformed time variables with theoretical probability distributions

```{r message=FALSE, warning=FALSE, include=FALSE}
write_csv(serp, 'data/serp.csv')
write_csv(source_features, 'data/source_features.csv')
write_csv(relevant, 'data/reliable.csv')
write_csv(irrelevant, 'data/nonreliable.csv')

data = read.table('data/Variables_L2_EMME_clean_complete.csv', 
                 sep = ';', 
                 dec = ',',
                 encoding = 'UTF-8',
                 header = 1) %>%
  left_join(serp %>%
              rename(serp_clean = EventDuration,
                     serp_clean_log = log_EventDuration),
            by = 'Participant') %>%
  left_join(source_features %>%
              rename(source_features_clean = EventDuration,
                     source_features_clean_log = log_EventDuration),
            by = 'Participant') %>%
  left_join(relevant %>%
              rename(reliable = EventDuration) %>%
              select(-AOI),
            by = 'Participant') %>%
  left_join(irrelevant %>%
              rename(nonreliable = EventDuration) %>%
              select(c(Participant, nonreliable)),
            by = 'Participant') %>%
  mutate(group = ifelse(Participant %>% str_detect('EMME'), 
                        'EMME', 
                        'VIDEO'))

write.xlsx(data, 'data/data.xlsx')
```

# Main Analysis

## Research Questions 1a and 1b

To answer the research questions RQ1a and RQ1b, two linear models were fit: the first one was a multiple linear regression model with the natural logarithm of fixation duration on SERP as response and Group (two levels: EMME and VIDEO), L2 level, and self-perceived strategic behavior as predictors; the second one was a mixed-effects model with total fixation duration on source features, on reliable and non-reliable pages, as response, and Group, L2 level, and self-perceived strategic behavior as predictors with random intercepts for participants.

The first model shows no statistically significant effect when all the possible interactions are considered. When interactions are removed from the model, it shows a statistically significant effect of Group ($\beta=-0.67, p=0.001,95\% CI=[-1.06, -0.28], R^2=.19, R^2 adjusted=.15$) (see Table 1).

The second model shows a similar pattern: no statistically significant effects when the interactions are considered and a statistically significant effect of Group ($\beta=56121.42, p=0.040,95\% CI=[2604.90, 109637.94], Marginal R^2=.12, Conditional R^2=.77$) when the interactions are removed from the model (see Table 2).

```{r message=FALSE, warning=FALSE, include=FALSE}
# Fit model 1 for RQ1
rq1_model1 = data %>%
  lm(serp_clean_log ~ group + lextale + survey, data = .)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Table 1
# tab_model(rq1_model1)
```

### Figure 3

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure3 = get_model_data(rq1_model1, 'eff')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .15) +
  xlab('Group') + 
  ylab('Fixation duration on SERP (log(ms))')

ggsave('figures/Figure3.png', 
       figure3,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure3
```

*Figure 3*. Log of total lenght of fixations predicted by Group

```{r message=FALSE, warning=FALSE, include=FALSE}
# Fit model 2 for RQ1
rq1_model2 = data %>%
  pivot_longer(c(reliable, nonreliable), 
               names_to = 'reliability',
               values_to = 'duration') %>%
  lmer(duration ~ group + lextale + survey + (1|Participant), 
       data = .)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
# Table 2
# tab_model(rq1_model2)
```

### Figure 4

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model

figure4 = get_model_data(rq1_model2, 'pred')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .2) +
  xlab('Group') + 
  ylab(str_wrap(
    'Fixation duration on reliable/non-reliable pages (ms)',
    45))

ggsave('figures/Figure4.png', 
       figure4,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure4
```

*Figure 4*. Fixation duration on reliable/non-reliable pages predicted by Group

## Research Questions 2a, 2b and 2c

To answer the reserch questions RQ2a, RQ2b, and RQ2c, three linear models were fit: the first with the argumentation scores as response and Group, English level, Fixation duration on SERP and fixation duration on source features as predictors; the second model with smt scores as response and Group, English level, Fixation duration on SERP and fixation duration on source features as predictors; and the third model, a mixed-effects model, with scores on the pre and post tests as response, Group, English level, Fixation duration on SERP, Fixation duration on source features, and moment (pre and post) as predictors, and random intercepts for participants.

The first model ($R^2=0.412, R^2 adjusted=0.196$) shows statistically significant effects of Fixation duration on SERP ($\beta=-207.00, p=0.040,95\% CI=[-403.65, -10.36]$) and Fixation duration on source features ($\beta=-233.13, p=0.025,95\% CI=[-435.59, -30.66]$) (Figures 5 and 6). Additionally, there are statistically significant interactions between Group and Fixation duration on source features ($\beta=-245.26, p=0.044,95\% CI=[7.19, 483.32]$), English level and Fixation duration on source features ($\beta=2.71, p=0.047,95\% CI=[0.04, 5.38]$), and Fixation duration on SERP and Fixation duration on source features ($\beta=21.17, p=0.030,95\% CI=[2.13, 40.22]$) (Table 3 and Figures 7 to 9).

The second model ($R^2=0.64, R^2 adusted=0.514$) shows statistically significant effects for all predictors and interactions (see Table 4 and Figures 10 to 23).

The third model ($Marginal R^2=0.167, Conditional R^2=0.436$) shows statistically significant effects of English level ($\beta=0.05, p=0.025, 95\%CI=[0.01, 0.10]$), Fixation duration on source features ($\beta=-0.95, p=0.020, 95\%CI=[-1.75, -0.15]$), and Moment ($\beta=-0.90, p=0.002, 95\%CI=[-1.47, -0.33]$), see Table 5.

```{r message=FALSE, warning=FALSE, include=FALSE}
# Fit model 1 for RQ2
rq2_model1 = data %>%
  lm(argumentation ~ group * lextale * serp_clean_log * source_features_clean_log, data = .)

# Fit model 2 for RQ2
rq2_model2 = data %>%
  lm(smt ~ group * lextale * serp_clean_log * source_features_clean_log, data = .)

# Fit model 3 for RQ2
rq2_model3 = data %>%
  pivot_longer(c(pre, post), 
               names_to = 'preposttest',
               values_to = 'response') %>%
  lmer(response ~ group + lextale + serp_clean_log + source_features_clean_log + preposttest + (1|Participant), 
       data = .)
```

```{r echo=FALSE}
# Table 3
# tab_model(rq2_model1)
# Table 4
# tab_model(rq2_model2)
# Table 5
# tab_model(rq2_model3)
```

### Figure 5

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure5 = get_model_data(rq2_model1, 'eff')$serp_clean_log %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab('Argumentation score')

ggsave('figures/Figure5.png', 
       figure5,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure5
```

*Figure 5*. *Argumentation scores predicted by Fixation duration on SERP*

### Figure 6

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure6 = get_model_data(rq2_model1, 'eff')$source_features %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on the Source Features (log(ms))') + 
  ylab('Argumentation score')

ggsave('figures/Figure6.png', 
       figure6,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure6
```

*Figure 6*. *Argumentation score predicted by Fixation duraton on the Source Features*

### Figure 7

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure7 = get_model_data(rq2_model1, 'int')[[4]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Argumentation score',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure7.png', 
       figure7,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure7
```

*Figure 7*. Interaction between Group and Fixation duration on source features

### Figure 8

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure8 = get_model_data(rq2_model1, 'int')[[5]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Argumentation score',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure8.png', 
       figure8,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure8
```

*Figure 8*. Interaction between English level and Fixation duration on source features

### Figure 9

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure9 = get_model_data(rq2_model1, 'int')[[6]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab(str_wrap(
    'Argumentation score',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure9.png', 
       figure9,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure9
```

*Figure 9*. Interaction between Fixation duration on SERP and Fixation duration on source features

### Figure 10

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure10 = get_model_data(rq2_model2, 'eff')$group %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2))) +
  geom_errorbar(width = .1) +
  geom_point() +
  geom_text(nudge_x = .15) +
  xlab('Group') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure10.png', 
       figure10,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure10
```

*Figure 10*. Scores on the Source Memory Task predicted by Group

### Figure 11

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure11 = get_model_data(rq2_model2, 'eff')$lextale %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure11.png', 
       figure11,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure11
```

*Figure 11*. Scores on the Source Memory Task predicted by English level

### Figure 12

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure12 = get_model_data(rq2_model2, 'eff')$serp_clean_log %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure12.png', 
       figure12,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure12
```

*Figure 12*. Scores on the Source Memory Task predicted by Fixation duration on SERP

### Figure 13

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure13 = get_model_data(rq2_model2, 'eff')$source_features_clean_log %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high)) +
  geom_line(linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on the Source Features') + 
  ylab('Scores on the Source Memory Task')

ggsave('figures/Figure13.png', 
       figure13,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure13
```

*Figure 13*. Scores on the Source Memory Task predicted by Fixation duration on the Source Features

### Figure 14

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure14 = get_model_data(rq2_model2, 'int')[[1]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('English level',
                  18))

ggsave('figures/Figure14.png', 
       figure14,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure14
```

*Figure 14*. Interaction between Group and English level

### Figure 15

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure15 = get_model_data(rq2_model2, 'int')[[2]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on SERP (log(ms))',
                  18))

ggsave('figures/Figure15.png', 
       figure15,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure15
```

*Figure 15*. Interaction between Group and Fixation duration on SERP

### Figure 16

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure16 = get_model_data(rq2_model2, 'int')[[3]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on SERP (log(ms))',
                  18))

ggsave('figures/Figure16.png', 
       figure16,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure16
```

*Figure 16*. Interaction between English level and Fixation duration on SERP

### Figure 17

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure17 = get_model_data(rq2_model2, 'int')[[4]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO')) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = .6)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure17.png', 
       figure17,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure17
```

*Figure 17*. Interaction between Group and Fixation duration on source features

### Figure 18

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure18 = get_model_data(rq2_model2, 'int')[[5]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure18.png', 
       figure18,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure18
```

*Figure 18*. Interaction between English level and Fixation duration on source features

### Figure 19

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure19 = get_model_data(rq2_model2, 'int')[[6]] %>%
  as_tibble() %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('Fixation duration on SERP (log(ms))') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on source features (log(ms))',
                  18))

ggsave('figures/Figure19.png', 
       figure19,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure19
```

*Figure 19*. Interaction between Fixation duration on SERP and Fixation duration on source features

### Figure 20

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure20 = get_model_data(rq2_model2, 'int')[[7]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO'),
         facet = facet %>% 
           str_replace_all('serp_clean_log',
                           str_wrap('Fixation duration on SERP', 20))) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = 1)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('English level',
                  18)) + 
  facet_grid(cols = vars(facet))

ggsave('figures/Figure20.png', 
       figure20,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure20
```

*Figure 20*. Interaction between Group, English level and Fixation duration on SERP

### Figure 21

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure21 = get_model_data(rq2_model2, 'int')[[8]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO'),
         facet = facet %>% 
           str_replace_all('source_features_clean_log',
                           str_wrap('Fixation duration on source features', 20))) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = 1)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('English level',
                  18)) + 
  facet_grid(cols = vars(facet))

ggsave('figures/Figure21.png', 
       figure21,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure21
```

### Figure 22

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure22 = get_model_data(rq2_model2, 'int')[[9]] %>%
  as_tibble() %>%
  mutate(x = x %>% 
           as_factor() %>%
           recode(`1` = 'EMME', `2` = 'VIDEO'),
         facet = facet %>% 
           str_replace_all('source_features_clean_log',
                           str_wrap('Fixation duration on source features', 20))) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high, 
             label = round(predicted, 2),
             color = group)) +
  geom_errorbar(width = .1, position = position_dodge(width = .2)) +
  geom_point(position = position_dodge(width = .2)) +
  geom_text(position = position_dodge(width = 1)) +
  xlab('Group') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on SERP',
                  18)) + 
  facet_grid(cols = vars(facet))

ggsave('figures/Figure22.png', 
       figure22,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure22
```

### Figure 23

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Plot model
figure23 = get_model_data(rq2_model2, 'int')[[10]] %>%
  as_tibble() %>%
  mutate(facet = facet %>% 
           str_replace_all('source_features_clean_log',
                           str_wrap('Fixation duration on source features', 20))) %>%
  ggplot(aes(x, 
             predicted, 
             ymin = conf.low, 
             ymax = conf.high,
             group = group)) +
  geom_line(aes(color = group), linewidth = 1) +
  geom_ribbon(alpha = .2) +
  xlab('English level') + 
  ylab(str_wrap(
    'Scores on the Source Memory Task',
    45)) +
  scale_color_brewer(palette = 'Dark2') +
  theme(legend.title = element_text()) +
  labs(color = 
         str_wrap('Fixation duration on SERP (log(ms))',
                  18)) +
  facet_grid(cols = vars(facet))

ggsave('figures/Figure23.png', 
       figure23,
       device = 'png', 
       width = 16, 
       height = 9, 
       units = 'cm', 
       dpi = 300)

figure23
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Plot model
plot_model(rq2_model2, type = 'int')[[11]]

```

### References
